Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-13 paper/abstraction/paper.tex
small tweaks

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
and non-templatized configurations, ensuring that a collection of low-level, local configurations
achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
failures, is extremely challenging.
%
%Worse, operators can never be sure that their templates correctly implement the policy. %
%Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which 
%policies they implement and for which topologies---other than those of the configurations obtained from 
%instantiating them.
%
In order to validate their templates, operators will typically first instantiate a template with appropriate
concrete parameters
and then test it using various scenarios.  In general, like in any complex software system, such testing is 
bound to be incomplete.
%Thus, operators validate templates by testing some concrete instantiations using
%simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. 
Moreover, even if network operators were to instantiate their templates using their initial network 
configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
provided would not hold as large networks evolve frequently over time.  In particular,
devices and links are sometimes taken offline for maintenance and sometimes added to expand
capacity.  Unfortunately, templates that
work for the current topology, may or may not work for future
topologies. Problems that occur may cause operators to make small, non-uniform changes to particular routers,
which defeats the purpose of a template system.  An even worse situation occurs when
operators feel obligated to update many devices to extend or change their network.  
Such network-wide configuration changes entail a great deal of risk and may be highly
disruptive in production networks with live traffic.
%Ideally, network engineers would like some guarantees about the future, namely that 
%certain types of changes to the network topology may be (1) made \emph{locally}, and do not require
%updates of routers far from the source of the change, and (2) do not violate key properties, such
%as fault tolerance.
%Updating the templates, if found to not work for a future topology,
%may cause trickle-down, network-wide configuration changes that are highly
%disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

During synthesis, our compiler performs an important analysis over abstract topologies to determine
the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
lower bound on the number of link failures require to disconnect one abstract location from another 
given the constraints specified by the abstract topology. Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
%% first analysis determines whether a user policy can be implemented correctly using BGP in
%% the face of failures (\ie, given any number of failures, will the traffic flow along one of the 
%% specified paths if such a path is available).  The second analysis determines the number of failures
%% required to disconnect one abstract location from another.  
%% Our synthesis algorithm comes with a strong guarantee come with a strong
%% guarantee:  when the templates are instantiated with parameters, giving rise to concrete configurations,
%% and those concrete configurations  {\em
%% any} concrete topology that complies with the abstract topology, the resulting
%% network will correctly implement the routing policy and meet the fault-tolerance
%% requirements.

@@

\section{Methane overview}
\label{sec:overview}

@@

Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
%It also means that our compiler subsumes those that operate only over concrete topologies.

>>>>

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein\thanks{Supported in part by National Science Foundation award
CNS-1161595.}}{UCLA}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
and non-templatized configurations, ensuring that a collection of low-level, local configurations
achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
failures, is extremely challenging.
%
%Worse, operators can never be sure that their templates correctly implement the policy. %
%Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which 
%policies they implement and for which topologies---other than those of the configurations obtained from 
%instantiating them.
%
In order to validate their templates, operators will typically first instantiate a template with appropriate
concrete parameters
and then test it using various scenarios.  In general, like in any complex software system, such testing is 
bound to be incomplete.
%Thus, operators validate templates by testing some concrete instantiations using
%simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. 
Moreover, even if network operators were to instantiate their templates using their initial network 
configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
provided would not hold as large networks evolve frequently over time.  In particular,
devices and links are sometimes taken offline for maintenance and sometimes added to expand
capacity.  Unfortunately, templates that
work for the current topology may or may not work for future
topologies. Problems that occur may cause operators to make small, non-uniform changes to particular router configurations,
which defeats the purpose of a template system.  An even worse situation occurs when
operators feel obligated to update many devices to extend or change their network.  
Such network-wide configuration changes entail a great deal of risk and may be highly
disruptive in production networks with live traffic.
%Ideally, network engineers would like some guarantees about the future, namely that 
%certain types of changes to the network topology may be (1) made \emph{locally}, and do not require
%updates of routers far from the source of the change, and (2) do not violate key properties, such
%as fault tolerance.
%Updating the templates, if found to not work for a future topology,
%may cause trickle-down, network-wide configuration changes that are highly
%disruptive in production networks with live traffic.
%Building sophisticated tools for validating templates is difficult

@@

During synthesis, our compiler performs an analysis over abstract topologies to determine
the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
lower bound on the number of link failures require to disconnect one abstract location from another 
given the constraints specified by the abstract topology. Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
%% first analysis determines whether a user policy can be implemented correctly using BGP in
%% the face of failures (\ie, given any number of failures, will the traffic flow along one of the 
%% specified paths if such a path is available).  The second analysis determines the number of failures
%% required to disconnect one abstract location from another.  
%% Our synthesis algorithm comes with a strong guarantee come with a strong
%% guarantee:  when the templates are instantiated with parameters, giving rise to concrete configurations,
%% and those concrete configurations  {\em
%% any} concrete topology that complies with the abstract topology, the resulting
%% network will correctly implement the routing policy and meet the fault-tolerance
%% requirements.

@@

\section{Propane/AT overview}
\label{sec:overview}

@@

Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network cannot evolve while others can.
%It also means that our compiler subsumes those that operate only over concrete topologies.
